Multi-fluids for Representing Sub-filter-scale Convection

### 2020-07-03 submit3/makeFigs/RCE_singleColumn.tex
First draft of revisions and responses to second set of reviews from reviewer 1. Still to respond to reviewer 2. I have currently not followed all of Dan's suggestions because Dan's work should go into Dan's first author papers. I still need to reponsd to and revise based on reviewer 2. I also need to add a couple of lines about the boundary layer depth for the RCE test case.

\usepackage{babel}
\begin{document}
\setlength\tabcolsep{0.5pt}%
\begin{tabular}{ccccc}
$\sigma_{1}$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
\multicolumn{5}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $b_{ij}^{T}=b_{i}$,
\hspace{6pt}  $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ 
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/P}\tabularnewline
\multicolumn{5}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$,
\hspace{6pt} $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ 
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/P}\tabularnewline
\end{tabular}
\end{document}

>>>>

\usepackage{babel}
\begin{document}
\setlength\tabcolsep{0.5pt}%
\begin{tabular}{ccccc}
$\sigma_{1}$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
\multicolumn{5}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $b_{ij}^{T}=b_{i}$,
\hspace{6pt}  $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ 
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/P}\tabularnewline
\multicolumn{5}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$,
\hspace{6pt} $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ 
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/P}\tabularnewline
\end{tabular}
\end{document}

### 2020-07-03 submit3/makeFigs/bubble.tex
First draft of revisions and responses to second set of reviews from reviewer 1. Still to respond to reviewer 2. I have currently not followed all of Dan's suggestions because Dan's work should go into Dan's first author papers. I still need to reponsd to and revise based on reviewer 2. I also need to add a couple of lines about the boundary layer depth for the RCE test case.

%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,british,times]{article}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[pdftex,a4paper]{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\pagestyle{empty}
\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}
\usepackage{calc}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear]{natbib}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage { fancybox}
\usepackage[pdftex]{graphicx,color}
\usepackage{rotating}
\newcommand{\nicefrac}[2]{\ensuremath ^{#1}\!\!/\!_{#2}}
\usepackage { fancybox}
\usepackage[export]{adjustbox}
\usepackage{amsmath}

@@

\usepackage{babel}
\begin{document}
\setlength\tabcolsep{0.5pt}%
\begin{tabular}{ccccc}
$\sigma_{1}$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
\multicolumn{5}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $b_{ij}^{T}=b_{i}$,
\hspace{6pt}  $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ 
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/P}\tabularnewline
\multicolumn{5}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$,
\hspace{6pt} $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ 
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/P}\tabularnewline
\end{tabular}
\end{document}

>>>>

%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,british,times]{article}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[pdftex,a4paper]{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\pagestyle{empty}
\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear]{natbib}

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage { fancybox}
\usepackage[pdftex]{graphicx,color}
\usepackage{rotating}
\newcommand{\nicefrac}[2]{\ensuremath ^{#1}\!\!/\!_{#2}}
\usepackage { fancybox}
\usepackage[export]{adjustbox}
\usepackage{amsmath}

@@

\usepackage{babel}
\begin{document}
\includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/0/bP}

\hspace{2cm}\raisebox{3cm}[0cm][0cm]{$t=0$ s}

\includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/500/bP}

\hspace{2cm}\raisebox{4cm}[0cm][0cm]{$t=500$ s}

\includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/1000/bP}

\hspace{2cm}\raisebox{5cm}[0cm][0cm]{$t=1000$ s}

\includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}
\end{document}
